Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing

### 2021-02-20 Dissonance_Santiago_v3/Dissonance_Santiago_v3.Rmd
Knitted REAMDE.Rmd and v3 of paper after checking data package

```{r install-data-package, include=FALSE}
# Run only once if needed
devtools::install_github("paezha/Mode-Dissonance-and-Subjective-Wellbeing", subdir = "ModeDissonanceSantiago")
```

```{r}
library(ModeDissonanceSantiago)
```

@@

```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "G", "H", "E", "F", "B", "C", "D"),
                                                   labels = c("Car", "Bicycle", "Walk", "Metro", "Bus", "Taxi", "Colectivo", "Motorcycle")),
                                        fill = USED)) +
  geom_bar() +
  xlab("Primary Mode of Travel") +
  scale_fill_manual(values = c("A" = "#F8766D", 
                               "G" = "#00BA38", "H" = "#00BA38", 
                               "E" = "#619CFF", "F" = "#619CFF", 
                               "B" = "#C77CFF", "C" = "#C77CFF", "D" = "#C77CFF")) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

>>>>

```{r install-data-package, include=FALSE}
# Run only once if needed
#devtools::install_github("paezha/Mode-Dissonance-and-Subjective-Wellbeing", subdir = "ModeDissonanceSantiago")
```

```{r load-data-package, include=FALSE}
library(ModeDissonanceSantiago)
```

@@

```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
mode_plot1 <- ggplot(data = Dissonance_Santiago, aes(x = factor(USED, levels = c("A", "G", "H", "E", "F", "B", "C", "D"),
                                                   labels = c("Car", "Bicycle", "Walk", "Metro", "Bus", "Taxi", "Colectivo", "Motorcycle")),
                                        fill = USED)) +
  geom_bar() +
  xlab("Primary Mode of Travel") +
  scale_fill_manual(values = c("A" = "#F8766D", 
                               "G" = "#00BA38", "H" = "#00BA38", 
                               "E" = "#619CFF", "F" = "#619CFF", 
                               "B" = "#C77CFF", "C" = "#C77CFF", "D" = "#C77CFF")) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

### 2021-02-20 Dissonance_Santiago_v3/Dissonance_Santiago_v3.tex
Knitted REAMDE.Rmd and v3 of paper after checking data package

Please note that this document was prepared using R Markdown and is an
example of reproducible research (Brunsdon and Comber, 2020). The R
Markdown file, along with the data file needed to reproduce the
analysis, are available for
download\footnote{\url{https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg}}.

>>>>

Please note that this document was prepared using R Markdown and is an
example of reproducible research (Brunsdon and Comber, 2020). The R
Markdown file, along with the data file needed to reproduce the
analysis, are available for
download\footnote{\url{https://github.com/paezha/Mode-Dissonance-and-Subjective-Wellbeing}}.

### 2021-02-20 README.Rmd
Knitted REAMDE.Rmd and v3 of paper after checking data package

```{r table-cross-tabulation-results-with-instrumental, echo = FALSE, eval=FALSE}
kable(xtab_results,
      "latex",
      digits = 2,
      booktabs = TRUE,
      caption = "\\label{tab:cross-tabulation-results-with-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("Variable", 
                    "Freedom", "$\\chi^2$ p-val", 
                    "Enjoyment", "$\\chi^2$ p-val",
                    "Happiness", "$\\chi^2$ p-val",
                    "Safety", "$\\chi^2$ p-val",
                    "Time", "$\\chi^2$ p-val",
                    "Efficiency", "$\\chi^2$ p-val")) %>%
  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
  pack_rows("Age", 1, 3) %>%
  pack_rows("Education", 4, 6) %>%
  pack_rows("Income", 7, 9) %>%
  pack_rows("Mode", 10, 13) %>%
  pack_rows("Commute Time", 14, 17)  %>%
  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
  landscape()
```

```{r table-cross-tabulation-results-without-instrumental, echo = FALSE}
kable(xtab_results,
      "latex",
      digits = 2,
      booktabs = TRUE,
      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various affective values",
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("Variable", 
                    "Freedom", "$\\chi^2$ p-val", 
                    "Enjoyment", "$\\chi^2$ p-val",
                    "Happiness", "$\\chi^2$ p-val",
                    "Poverty", "$\\chi^2$ p-val",
                    "Luxury", "$\\chi^2$ p-val",
                    "Status", "$\\chi^2$ p-val")) %>%
  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
  pack_rows("Age", 1, 3) %>%
  pack_rows("Education", 4, 6) %>%
  pack_rows("Income", 7, 9) %>%
  pack_rows("Mode", 10, 13) %>%
  pack_rows("Commute Time", 14, 17)  %>%
  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
  landscape()
```

>>>>

```{r table-cross-tabulation-results-with-instrumental, echo = FALSE, eval=FALSE}
kable(xtab_results,
      "html",
      digits = 2,
      booktabs = TRUE,
      caption = "\\label{tab:cross-tabulation-results-with-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("Variable", 
                    "Freedom", "$\\chi^2$ p-val", 
                    "Enjoyment", "$\\chi^2$ p-val",
                    "Happiness", "$\\chi^2$ p-val",
                    "Safety", "$\\chi^2$ p-val",
                    "Time", "$\\chi^2$ p-val",
                    "Efficiency", "$\\chi^2$ p-val")) %>%
  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
  pack_rows("Age", 1, 3) %>%
  pack_rows("Education", 4, 6) %>%
  pack_rows("Income", 7, 9) %>%
  pack_rows("Mode", 10, 13) %>%
  pack_rows("Commute Time", 14, 17)  %>%
  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
  landscape()
```

```{r table-cross-tabulation-results-without-instrumental, echo = FALSE}
kable(xtab_results,
      "html",
      digits = 2,
      booktabs = TRUE,
      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various affective values",
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("Variable", 
                    "Freedom", "$\\chi^2$ p-val", 
                    "Enjoyment", "$\\chi^2$ p-val",
                    "Happiness", "$\\chi^2$ p-val",
                    "Poverty", "$\\chi^2$ p-val",
                    "Luxury", "$\\chi^2$ p-val",
                    "Status", "$\\chi^2$ p-val")) %>%
  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
  pack_rows("Age", 1, 3) %>%
  pack_rows("Education", 4, 6) %>%
  pack_rows("Income", 7, 9) %>%
  pack_rows("Mode", 10, 13) %>%
  pack_rows("Commute Time", 14, 17)  %>%
  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
  landscape()
```
